Response to the defense feedback

### 2021-06-01 Chapter-6/Chapter-6.tex
Updates from Overleaf

\subsection*{Design Choices.} At the early stage of the project, we use SMT solvers to get the solutions of constraints. However, we find for some ciphers (RSA), \detect{} times out after several days. The profiling result shows that it is spending most its time in Z3. Later, we use a sampling method to detect side-channel leakages. The sampling method seems simple and may miss some leakages in theory. However, the evaluation result shows \detect{} can identify all leakages found by the previous work~\cite{203878,236338,Brotzman19Casym}.

@@

\subsection*{Leakages.} While recent works have reported lots of potential side-channel vulnerabilities, most of them are not patched by developers. The DES implementation of OpenSSL has several sensitive leakages, but given the end life status of DES, it is still unpatched for the worth of engineering effort. After we manually analyze these leakage sites, we find many of them leak very little or useless information (e.g., the length of big numbers), which partially explain why developers are not interested in fix all the leakages. 
\section{Precise Analysis on Single-trace Attacks}
While recent work found many side-channel vulnerabilities,
we note that many of them have not been patched by developers.
Side-channels are ubiquitous in software and it would be difficult to fix all of them.
We need a tool that estimates the sensitivity of each vulnerability
so software engineers can focus on
``severe'' leakages. For example, \tool{} reports that
the modular exponentiation using square and multiply algorithms can
leak more information than a key validation function.

@@

\ctool{} requires the random input variables to be independent and identically distributed (i.i.d.). That's why I applied a blackbox fuzzing instead of a coverage-guided fuzzing. As long as each time we get a random input from the whole input space (Populations) that is independent of the previous input, the input variables should satisfy the i.i.d. assumption. For AES-128 encryption, each time we randomly generate a 128 bit key from $0$ to $2^{128}$, the sequence of key values follows the i.i.d. assumption. The situation is a little different for machine learning libraries. In the dissertation, we evaluated \ctool{} on a deep learning model. Each time, we randomly select an item from a dataset (Samples). If the dataset is biased, then we can not get the correct results. The good news is that the most well-known data set in machine learning is i.i.d.. i.i.d. is the foundation of supervised machine learning algorithms. In my dissertation, we used MINIST, a well-known handwriting dataset. The dataset is widely used in many supervised machine learning tasks.  We believe the dataset is i.i.d..

>>>>

\subsection*{Design Choices} At the early stage of the project, we use SMT solvers to get the solutions of constraints. However, we find for some ciphers (RSA), \detect{} times out after several days. The profiling result shows that it is spending most its time in Z3. Later, we use a sampling method to detect side-channel leakages. The sampling method seems simple and may miss some leakages in theory. However, the evaluation result shows \detect{} can identify all leakages found by the previous work~\cite{203878,236338,Brotzman19Casym}.

@@

\subsection*{Leakages} While recent works have reported lots of potential side-channel vulnerabilities, most of them are not patched by developers. The DES implementation of OpenSSL has several sensitive leakages, but given the end life status of DES, it is still unpatched for the worth of engineering effort. After we manually analyze these leakage sites, we find many of them leak very little or useless information (e.g., the length of big numbers), which partially explain why developers are not interested in fix all the leakages. 
\section{Precise Analysis on Single-trace Attacks}
While recent work found many side-channel vulnerabilities,
we note that many of them have not been patched by developers.
Side-channels are ubiquitous in software and it would be difficult to fix all of them.
We need a tool that estimates the sensitivity of each vulnerability
so software engineers can focus on
``severe'' leakages. For example, \tool{} reports that
the modular exponentiation using square and multiply algorithms can
leak more information than a key validation function.

@@

\ctool{} requires the random input variables to be independent and identically distributed (i.i.d.). That's why I apply a black box fuzzing instead of a coverage-guided fuzzing. As long as each time we get a random input from the whole input space (Populations) that is independent of the previous input, the input variables should satisfy the i.i.d. assumption. For AES-128 encryption, each time we randomly generate a 128 bit key from $0$ to $2^{128}$, the sequence of key values follows the i.i.d. assumption. The situation is a little different for machine learning libraries. In the dissertation, we evaluated \ctool{} on a deep learning model. Each time, we randomly select an item from a dataset (Samples). If the dataset is biased, then we can not get correct results. The good news is that the most well-known data set in machine learning is i.i.d.. i.i.d. is the foundation of supervised machine learning algorithms. In my dissertation, we used MINIST, a well-known handwriting dataset. The dataset is widely used in many supervised machine learning tasks.  We believe the i.i.d. assumption holds under the circumstance.
